---
title: 'Homework 3'
author: Tara Munjuluri
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).

1. Finish the in-class practice in Slides 3-12 in "Lecture 2-2-Practice for git", link: https://yumouqiu.github.io/DS202-Spring2023/Practice/practice01.html  
    a. Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" with your name.  
    b. In the RMarkdown file, write down table of team members, and their github repository links;   
    Tara Munjuluri:https://github.com/TaraMunjuluri/practice1-TaraMunjuluri
    Aditi Nachnani: https://github.com/AditiN2003/practice1-aditin2003.git
    Snehal Arla:https://github.com/Snehal2301/Graph


the number of successful pull requests you made, and the github repository to which you requested a change;  
Number of pull requests made: 2
Requested changes:Aditi Nachnani, Snehal Arla

the number of pull requests you accepted, and the github repository from which you accepted.  
Number of pull requests accepted: 2
Repositories accepted from: Aditi Nachnani, Snehal Arla

c. Write down a list with at least 3 tips of how to make working with git/github easier  
1.To make commits after changes to know what updates/changes have been made
2.To make sure some sort of change has been made before trying to make a pull request and making sure you have not created to repositories under the same branch to make pull requests easier
3. To create separate branches when needed to do devlopment and testing in a separate place


2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
```{r}
gapMinder <- read.csv("gapminder-5060 (1).csv")
```
```{r}
summary(gapMinder)
```
```{r}
subset_gapMinder <- subset(gapMinder, country %in% c("Australia","United States"))



```



```{r}
library(ggplot2)
ggplot(data = subset_gapMinder, aes(x = lifeExp, y = gdpPercap)) +
  geom_point(aes(color = country))+
   labs(title = "Life Expectancy vs. GDP per capita by Country",
       x = "Life Expectancy",
       y = "GDP per capita") +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73")) +
  scale_x_continuous(limits = c(0, 120)) +
  scale_y_continuous(limits = c(100, 20000))
```
3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
     I consider data science as analysis of information to find useful patterns. An example I consider as data science is determining predictions for the weather by analyzing previous weather tempuratures. This is helpful so that we can determine the forecast of the days ahead. These patterns focused on extracting knowledge from typically large data sets and applying the knowledge and insights from that data to solve many problems. Many real-world examples including analyzing algorithms in Netflix to provide suggetions for movies and suggestions for songs in spotify
https://www.climate.gov/maps-data/dataset/future-climate-projections-graphs-maps
1,Form a hypothesis 
2.Make observations 
3.Analyze and interpret the data
4.Draw conclusions
5.Publish results that can be validated with further experiments 
6.Repeat this process

    

Note: your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. Including the link to the image is the tricky part here. Make sure that you don't use any file structure that depends on your computing environment.


For the submission: submit your solution in an **R Markdown file** and (just for insurance) submit the corresponding html (or Word) file with it. 


