---
title: 'Homework 3'
author: Tara Munjuluri
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Due: 2/17/2022 before 11:59pm. Submit in Canvas (file upload).

1. Finish the in-class practice in Slides 3-12 in "Lecture 2-2-Practice for git", link: https://yumouqiu.github.io/DS202-Spring2023/Practice/practice01.html  
    a. Download the RMarkdown file with these homework instructions to use as a template for your work. Make sure to replace "Your Name" with your name.  
    b. In the RMarkdown file, write down table of team members, and their github repository links;   
    Tara Munjuluri:https://github.com/TaraMunjuluri/practice1-TaraMunjuluri
    Aditi Nachnani: https://github.com/AditiN2003/practice1-aditin2003.git
    Snehal Arla: https://github.com/Snehal2301/practice1-your-Snehal2301

the number of successful pull requests you made, and the github repository to which you requested a change;  
Number of pull requests made: 2
Requested changes:Aditi Nachnani, Snehal Arla
the number of pull requests you accepted, and the github repository from which you accepted.  
Number of pull requests accepted: 2
Repositories accepted from: Aditi Nachnani, Snehal Arla
    c. Write down a list with at least 3 tips of how to make working with git/github easier  
1.To make commits after changes to know what updates/changes have been made
2.To make sure some sort of change has been made before trying to make a pull request and making sure you have not created to repositories under the same branch to make pull requests easier
3. To create separate branches when needed to do devlopment and testing in a separate place

2. Generate the graph of LifExp vs. gdpPercap for US, Canada (fixed data) and Australia by RMarkdown based on the data set "gapminder-5060", like what we did in the class.  
Please use Github to collaborate on this problem. For example, one member can create the plot of US in his/her repository. The other member will fork this repository, add the result for the second country, and make a pull request for merging into the main repository. Each member should at least analyze one country and make at least one pull request. **Please submit the RMarkdown file, the output file, and the screen shot of the successful pull request and the merge.**

```{r}
gapMinder <- read.csv("gapminder-5060.csv",)
```
```{r}
summary(gapMinder)
```
```{r}
subset_gapMinder <- subset(gapMinder, country %in% c("Australia", "Canada"))



3. Write a paragraph (~200 words) describing an example of what you consider data science. Write your paragraph in R Markdown. Include at least 
    a. one link to a chart or an image and 
    b. at least one itemized or enumerated list.
    
    I consider data science as analysis of information to find useful patterns. An example I consider as data science is determining predictions for the weather by analyzing previous weather tempuratures and patterns
    

Note: your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. Including the link to the image is the tricky part here. Make sure that you don't use any file structure that depends on your computing environment.


For the submission: submit your solution in an **R Markdown file** and (just for insurance) submit the corresponding html (or Word) file with it. 
